On Secure Delegation of SampBQP with a Classical Client

### 2019-11-21 longoutput.tex
Start rewriting long output

Here we describe the scheme between the classical client and an honest quantum server. This is similar to the underlying construction of \cite{mahadev_delegation}. We first preprocess the circuit using tools such as \cite{quant-ph/0301040}. We then follow \cite{kitaev2002classical} to reduce the problem to an instance of local Hamiltonian. Using tools from \cite{PhysRevA.93.022326}, the local Hamiltonian is written in a simple form. Then, NYI cuz we're stuck. \hannote{be more explicit}

First, for ease of notation, we write

@@

\begin{definition}
	Let $C(x)$ be a quantum circuit. Then let $H_{C(x)}$ be with the following properties: TODO
	\begin{itemize}
		\item can be written as...
		\item 0 eigenvalue ground state
		\item at least whatever eigenvalue in all other dimensions
		\item has ground state of a particular form we like
	\end{itemize}
\end{definition}

@@

>>>>

Here we lay our theoretical fundation by describing a reduction from $\SampBQP$ that we'll use throughout this paper.

First, for ease of notation, write

@@

\begin{definition}
	Let $C(x)$ be a quantum circuit. Then let $H_{C(x)}$ be with the following properties: TODO
	\begin{itemize}
		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$, where each $S$ has at most constantly many non-identity components.
		\item 0 eigenvalue ground state and has certain form TODO type it out
		\item at least whatever eigenvalue in all other dimensions
		\item has ground state of a particular form we like
	\end{itemize}
\end{definition}

@@

TODO Combine and rewrite the following subsections
